R for Clinical Study Reports and Submission

### 2021-10-27 slides/workshop-slides.Rmd
change break time

- Delivering TLFs in CSR (Yilong Zhang)
  + Session 1 (45 min)
  + Break (10 min)
  + Session 2 (45 min)
  + Break (20 min) 
- Clinical trial project (Nan Xiao)
  + Session 3 (30 min)
  + Break (10 min)
- eCTD submission package (Nan Xiao)
  + Session 4 (40 min)
  + Q&A (10 min)

@@

@@

# Break (20 min)

>>>>

- Delivering TLFs in CSR (Yilong Zhang)
  + Session 1 (45 min)
  + Break and/or Exercise (20 min)
  + Session 2 (45 min)
  + Break (10 min) 
- Clinical trial project (Nan Xiao)
  + Session 3 (30 min)
  + Break (10 min)
- eCTD submission package (Nan Xiao)
  + Session 4 (40 min)
  + Q&A (10 min)

@@

# Break and/or Exercise (20 min)

@@
